
%
% LaTeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%
% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{enumitem}
\setlist{noitemsep}
\setlist{nosep}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}


\begin{document}  % begin the content of the document
\sloppy{}  % this to relax whitespacing in favour of straight margins

% title on top of the document
\maintitle{Sep Taheri}

\vspace

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:sepehr.tah.at.gmail.dot.com}{sepehr.tah\mbox{}@\mbox{}gmail.com}\sbull
\textsmaller604-446-6292\sbull
\href{https://sepehr.ca}{sepehr.ca} (Personal blog) \sbull
\href{https://github.com/supsep}{SupSep} (Github) \sbull
\href{http://www.linkedin.com/in/supsep}{SupSep} (LinkedIn) 


\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title

Curious by nature, Sep is a proven leader, a Certified Scrum Master and an 
award-winning Software Engineer, as well as having an entrepreneurial
mind and a passion for continuous learning  and delivering value
by designing and developing well-tested, maintainable software.

\noindent\begin{itemize}
\item Built fault-tolerant and reliable software for an industry leading Intrusion Prevention System (IPS) responsible for defending critical infrastructure from cyber attacks in over 80 countries.
\item Improved team velocity by incorporating Planning Poker technique time-boxing the daily stand up meeting with both local and remote resources.
\item Conducted a code refactor for a product over several repositories which resulted in over 300,000 lines of code removed, without affecting user functionality.
\end{itemize}


\vspace{1em}
\spacedhrule{0em}{-0.4em}

\roottitle{Skills}
\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Software:}
  {Maven, Gradle,  Git (GitHub, GitLab and Gerrit), Docker, Static code analysis (Coverity, FindBugs, Infer and Protecode), Postman, Automation (Selenium, Cucumber, Protractor Test), Amazon Web Services (AWS), Wireshark, Eclipse, IntelliJ IDEA, Photoshop, synchronous messaging (JMS, ActiveMQ and RabbitMQ), OAuth.}

\inlineheadsection 
  {Languages:}
  {Java, Javascript, Scala, Python, Unix Shells (Sh, Bash and zsh), HTML5, CSS, and jQuery.}
  
\inlineheadsection 
  {Project Management Tools:}
  {JIRA, Confluence, CA Agile Central (f.k.a Rally), BugZilla, TestRail, CI/CD (Jenkins and TeamCity).}

\inlineheadsection 
  {Databases:}
  {Relational Databases (PostgreSQL, MySQL, Orcale SQL), Document-oriented databases (CouchDB and MongoDB).}
  
\inlineheadsection 
  {Operating Systems:}
  {Mac OSX, Linux (Debian Stretch and Ubuntu 14.04, 18.04), Virtual Machines (VMWare Workstation and Fusion, VirtualBox).}
  
\inlineheadsection 
  {Methodologies:}
  {Agile (Scrum and Kanban), Test Driven Development (TDD), Behaviour Driven Development (BDD), Waterfall, Lean Development.}
  

\vspace{1em}
\spacedhrule{0em}{-0.4em}

\roottitle{Experience}

\headedsection  % sets the header for the section and includes any subsections
  {{GE Digital, f.k.a Wurldtech Security Technologies}}
  {\textsc{Vancouver, Canada}} {%
  \headedsubsection
    {Senior Software Developer, Scrum Master}
    {Dec \apo17 -- Present}
   {\noindent
    
   \textbf{Technologies used:}   Debian 9, Ubuntu 18.04, Docker, Bottle, CouchDB, Selenium, Cucumber, Protractor, Selenium\begin{itemize}  
\item Scrum Master for two different teams in two different products located in two separate locations while maintaining developer role in both teams.
\item Influenced major architectural decisions for software release such as migrating OS and handling customer issues as first point of contact in engineering team.
\item Consistently provided QA milestones such as recreating a staging environment and conceived a complex upgrade framework for testing software version path permutations. 
\end{itemize}}
    
  \headedsubsection
    {Software Developer}
    {Mar \apo15 -- Dec \apo17}
    {\noindent
    
   \textbf{Technologies used:}   AngularJS 1, Restlet, Ubuntu 14.04, Kafka, Zookeeper, ActiveMQ, Akka, JMS, PostgreSQL, Postman, Hibernate, eBean, \begin{itemize}  
\item Led, designed and developed features spanning several teams and stacks for the \href{https://www.ge.com/digital/asset/opshield-ge-digital}OpShield, an industrial
grade firewall and router used for critical infrastructure, which analyzes data packets over numerous protocols (Layer
3 and 7 in the OSI Model).
\item Brought REST API into modernity by implementing ActiveMQ
with JMS, meeting OWASP specifications, implementing a data integrity check by verifying hashes and a full-stack real-time system statistics monitor using collectd.
\item Testing achievements include increasing unit test coverage to 85\% (from 50\%) through unit tests, creating a component test framework, adopting Continuous Integration using Jenkins and Gerrit, and BDD by creating system tests using Cucumber and Selenium.
\end{itemize}}
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://www.quotemedia.com/}{QuoteMedia, Inc.}}
  {\textsc{Vancouver, Canada}} {
  \headedsubsection
    {Junior Developer}
    {Mar \apo14 -- Mar \apo15}
    {\noindent
    
   \textbf{Technologies used:}   Java, Struts, Spring, JProfiler, WildFly (f.k.a JBoss), Bash, Oracle SQL, Nginx, SVN, BugZilla and TeamCity \begin{itemize}  
\item QuoteMedia is responsible for supervising and regulating securities and other financial instruments, of which provides quotes and dynamic charts, stock portfolio management and live news for numerous stock exchanges (including TSX).
\item Roles included implementing features, tests and fixes on QuoteTools API, a Java web suite built on Struts and JBoss 7, containing an extremely
fault-tolerant methodology, while balancing efficiency to provide real-time solutions to clients.
\item Impacted the product massively when rebuilding charting engine to produce SVG images which improved mobile
experience, reduced file size by 44\% and pushed rendering to client-side.
\end{itemize}}
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{http://arbutussolutions.com/}{Arbutus Solutions Ltd.}}
  {\textsc{Victoria, Canada}} {
  \headedsubsection
    {Web Developer}
    {Nov \apo13 -- Apr \apo14}
    {\noindent
    
   \textbf{Technologies used:}    HTML, Javascript, jQuery, SharePoint Designer and Server, and Adobe Photoshop.\begin{itemize}   
\item The internship was focused on helping designing implementing the \href{http://arbutussolutions.com/}{Arbutus Solutions} website, collaborated with additional remote developers.
\item The dynamic front-facing company website had features such as blogs, news and webinar management, was implemented with
\end{itemize}}
}

\vspace{1em}
\spacedhrule{0em}{-0.4em}

\roottitle{Certifications:}
\headedsection
  {\href{https://www.scrumalliance.org/}{Scrum Alliance}}
  {\textsc{Vancouver, Canada}} {
  \headedsubsection
    {Certified Scrum Master}
    {2017}
    {}
}

\headedsection
  {\href{https://www.sja.ca}{St. John Ambulance}}
  {\textsc{Vancouver, Canada}} {
  \headedsubsection
    {{Occupational First Aid Level 2 Certificate}}
    {2016}
    {}
}

\vspace{1em}
\spacedhrule{0em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{https://www.uvic.ca/}{University of Victoria}}
  {\textsc{Victoria, Canada}} {
  \headedsubsection
    {BSc -- Computer Science, with minor in Software Engineering}
    {2009 -- 2014}
    {\bodytext{Focused on network security, cryptography, systems engineering, fault tolerance, with additional attention on relational databases and data mining.}}
}

\vspace{1em}
\spacedhrule{0em}{-0.4em}

\roottitle{Personal Projects}
\inlineheadsection
  {UturnMail:}
  {Developed an email service that provides users with a supplementary
email address that automatically interacts with emails, and will relay important information to the user. For example, it would automatically active accounts for new accounts.
Implemented with Postfix SMTP, Courier IMAP with TLS encryption on Ubuntu 14.04 using Amazon Web Services.}

\vspace{0.5em}
\inlineheadsection
  {NHL Predictor:}
  {Wrote web crawler in Python that collected and preprocessed over
50,000 records of NHL seasons, teams and players since 1994 from several web sources and organized them
in CSV database. Created predictions from processed data by implementing several data mining algorithms.}

\vspace{1em}
\spacedhrule{0em}{-0.4em}

\roottitle{References}

\inlineheadsection
  {Available upon request.}

\end{document}

