%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Ping Identity} % Organization
    {Vancouver, Canada} % Location
    {Aug. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Slackbot responsible for running daily scrum, delivering manager reports with integrations into GitLab, Confluence and Company Calendar.}
        \item {24/7 On-call responsibilities include overseeing kubernetes clusters in several regions, promptly investigating incidents and producing a resolve within 15 minutes. }
        \item {Part of Product Security team rountinely conducting Security Risk Assessments SRAs, Threat data models and constant monitoring of vulnerabilitise using BlackDuck and NetSparker. }
        \item {Technologies used: Java, Struts, Spring, JProfiler, WildFly (f.k.a JBoss), Bash, Oracle SQL, Nginx, SVN, BugZilla and TeamCity. }
     \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer, Scrum Master} % Job title
    {GE f.k.a Wurldtech Security Technologies} % Organization
    {Vancouver, Canada} % Location
    {Mar. 2015 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Scrum Master for two different teams in two different products located in two separate locations while maintaining Lead Developer role .}
        \item {Influenced major architectural decisions for software release such as migrating OS and handling customer issues as first point of contact in engineering team.}
        \item {Brought REST API into modernity by implementing ActiveMQ
        with JMS, meeting OWASP specifications, implementing a data integrity check by verifying hashes and a full-stack real-time system statistics monitor using collectd.}
        \item {onsistently achieved testing milestones such as creating staging environments, conceived a complex upgrade framework for testing software version path permutations, increasing unit test coverage to 85\% (from 50\%) through unit tests, creating a component test framework, adopting Continuous Integration using Jenkins and Gerrit, and BDD by creating system tests using Cucumber and Selenium. }
        \item {Technologies used: Java, Restlet, Javascript, AngularJS 1, Ubuntu 14.04, PostgreSQL, Postman, Hibernate, eBean, Kafka, Zookeeper, ActiveMQ, Akka, JMS, Wireshark, JUnit, Mockito, Guice, Bash, Debian 9, Ubuntu 18.04, Python, Docker, Bottle, CouchDB, Protractor, JMeter.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {QuoteMedia Inc.} % Organization
    {Vancouver, Canada} % Location
    {Mar. 2014 - Mar. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {QuoteMedia is responsible for supervising and regulating securities and other financial instruments, of which provides quotes and dynamic charts, stock portfolio management and live news for numerous stock exchanges (including TSX).}
        \item {Roles included implementing features, tests and fixes on QuoteTools API, a Java web suite built on Struts and JBoss 7, containing an extremely
        fault-tolerant methodology, while balancing efficiency to provide real-time solutions to clients.}
        \item {Impacted the product massively when rebuilding charting engine to produce SVG images which improved mobile
        experience, reduced file size by 44\% and pushed rendering to client-side.}
        \item {Technologies used: Java, Struts, Spring, JProfiler, WildFly (f.k.a JBoss), Bash, Oracle SQL, Nginx, SVN, BugZilla and TeamCity. }
     \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Game Developer Intern at Global Internship Program} % Job title
    {NEXON} % Organization
    {Seoul, S.Korea \& LA, U.S.A} % Location
    {Jan. 2013 - Feb. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed in Cocos2d-x an action puzzle game(Dragon Buster) targeting U.S. market.}
        \item {Implemented API server which is communicating with game client and In-App Store, along with two other team members who wrote the game logic and designed game graphics.}
        \item {Won the 2nd prize in final evaluation.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
